### 2017-09-23 Risk analysis/Text/Layout/Layout/chapter2_methods.tex
Bit of progress

        \subsection{Economic significance and reservoir valuation}\label{sec:Reservoir_values}
        In this work, the generated structural models are to be assigned an economic significance in order to approach a real setting, in which hypothetical actors could have an interest in taking a decision, and thus, to evaluate the influence of the Bayesian inference of the decision-making process. Changes in Bayes actions are considered as a measure for this effect.\\
        For this purpose, it is assumed that a hydrocarbon reservoir system is represented by each geological model realization. These are typically comprised stratigraphically of at least one potential reservoir formation, succeeded by at least one sealing layer above. Additionally, a trapping mechanism is normally required (source?).\\
        The resulting reservoirs are to be valuated in a way that respective estimations on the basis of loss functions can be conducted, i.e. Bayesian decision theory is applicable. In the typical petroleum industrial setting, the main question is one of how much of the resource can be produced and how high the return on investment will be \citep{dean2007volumetric}.\\

@@

        Consequently, OOIP and ROV calculations represent the step following and using the results from computing the geological model, so that the realizations are assigned values that can be interpreted from a perspective of economic interest. The resulting values from numerous model runs are used as a base probability distribution for the true value, on which loss function estimation can be applied as described in Section \ref{sec:loss}.\\

        \subsubsection{Abstract valuation using scores in the one-dimensional case}
        - in the end: NPV

        - here: 1D abstract case: arbitrarily chosen "scoring-system" as a reservoir value measure

@@

>>>>

        \subsection{Economic significance and reservoir valuation}\label{sec:Reservoir_values}
        In this work, the generated structural models are to be assigned an economic significance in order to approach a real setting, in which hypothetical actors could have an interest in taking a decision, and thus, to evaluate the influence of the Bayesian inference of the decision-making process. Changes in Bayes actions are considered as a measure for this effect.\\
        For this purpose, it is assumed that a hydrocarbon reservoir system is represented by each geological model realization. These are typically comprised stratigraphically of at least one potential reservoir formation, succeeded by at least one sealing layer above. Additionally, a trapping mechanism is normally required (source?).\\
        The resulting reservoirs are to be valuated in a way that respective estimations on the basis of loss functions can be conducted, i.e. Bayesian decision theory is applicable. In the typical petroleum industrial setting, the main question is one of how much of the resource can be produced and how high the return on investment will be \citep{dean2007volumetric}.\\

        \subsubsection{Original oil-in-place and recoverable volumes as value measures}

@@

        Consequently, OOIP and ROV calculations represent the step following and using the results from computing the geological model, so that the realizations are assigned values that can be interpreted from a perspective of economic interest. The resulting values from numerous model runs are used as a base probability distribution for the true value, on which loss function estimation can be applied as described in Section \ref{sec:loss}.
        \subsubsection{Net present value}
        hmmm...

        \subsubsection{Abstract valuation using scores in the one-dimensional model}
        For the simplified 1D model that is described further below, OOIP and recoverable volume calculations are not applicable, as these require a 3D setting. Given only layer positions in one vertical dimension, it is resorted to an abstract way of reservoir valuation by defining a scoring system. The reservoir score is made dependent on three uncertain parameters which can be deduced from the 1D layer positions: (1) reservoir thickness, (2) reservoir top depth and (3) seal thickness.

@@

		\section{Designing a case-specific loss function}

		\section{Constructing a 1D geological reservoir model}

		\section{Constructing a full 3D geological reservoir model}
